Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-05-25 paper/main.Rmd
illustration of principle - made into one and 2 sd apart from mean

```{r plot-all-new3, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here. As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d). Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design."}

>>>>

```{r plot-all-new3, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here. As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d). Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.", dependson= "null4by2"}
